### 2017-05-29 doc/related.tex

More closely related is the recent work of \namecite{li2015visualizing}, who develop techniques 
for a deeper understanding of the activation patterns of RNNs, but focus on models with 
modern architectures trained on large scale data sets. More specifically, they train Long 
Short-Term Memory networks (LSTM) \cite{hochreiter1997long} 
for phrase level sentiment analysis 
and present novel methods 
to explore the inner workings of RNNs. They measure the salience of tokens
in sentences by taking the first-order derivatives of the loss with respect to the
word embeddings and provide evidence 
that LSTMs can learn to attend to important tokens in sentences. Furthermore,
they plot the activation values of hidden units through time using heat maps 
and visualize local semantic compositionality in RNNs. 
In comparison, the present work focuses more on exploring structure 
learning in RNNs and on developing methods for a comparative analysis between RNNs.

>>>>

More closely related is the recent work of \namecite{li2015visualizing}, who develop techniques 
for a deeper understanding of the activation patterns of RNNs, but focus on models with 
modern architectures trained on large scale data sets. More specifically, they train Long 
Short-Term Memory networks (LSTM) \cite{hochreiter1997long} 
for phrase level sentiment analysis 
and present novel methods 
to explore the inner workings of RNNs. They measure the salience of tokens
in sentences by taking the first-order derivatives of the loss with respect to the
word embeddings and provide evidence 
that LSTMs can learn to attend to important tokens in sentences. Furthermore,
they plot the activation values of hidden units through time using heat maps 
and visualize local semantic compositionality in RNNs. 
In comparison, the present work goes beyond the importance of single words and focuses more on exploring structure 
learning in RNNs, as well as on developing methods for a comparative analysis between RNNs that are focused on different modalities (language versus vision).
